Cybercrime and Online Video Games

### 2019-12-14 paper/paper.tex
Update paper.tex
updated paper + bib

\subsection{Sentiment Analysis}
One of our tasks was to analyze the intentions behind each comment, whether
they were criticizing the product or, on the contrary, if they were lauding
the product. For that, we decided to use a Python package provided by scikit-learn.org
We used 3 different machine learning techniques to classify each comment as
either positive or negative: Stochastic Gradient Descent (SGD), Naive Bayes, 
Support Vector machines (SVC). Each algorithm gives each comment a probability to be either positive or negative. 
We sum each algorithm's score and determine based on that score whether the comment is positive, negative or neutral. Below is a chart
showing the percentage of comments that were deemed positive, negative and neutral.

@@

\begin{figure*}[h]
\centering
\begin{subfigure}{.25\textwidth}
 	\centering
	\includegraphics[width = .4\linewidth]{ThreadCount.png}
	\caption{Thread Count}
\end{subfigure}%
\begin{subfigure}{.25\textwidth}
 	\centering
	\includegraphics[width=.4\linewidth]{CommentCount.png}
	\caption{Comment Count}
\end{subfigure}
\caption{Thread and Comment Pie Charts}
\end{figure*}

>>>>

\subsection{Sentiment Analysis}
One of our tasks was to analyze the intentions behind each comment, whether
they were criticizing the product or, on the contrary, if they were lauding
the product. For that, we decided to use a Python package provided by scikit-learn.org
We used 3 different machine learning techniques to classify each comment as
either positive or negative:
\begin{itemize}
  \item Stochastic Gradient Descent (SGD)
  \begin{equation*}
    E(w,b) = \frac{1}{n} \sum\limits_{i=1}^nL(y_i, f(x_i)) + \alpha R(w)
  \end{equation*} \cite{SGD}

  \item Naive Bayes
  \begin{equation*}
    \theta_yi = \frac{N_{yi} + \alpha}{N_y + \alpha n}
    \newline
    where\ N_yi = \sum_{x\in T} x_i\ and\ N_y = \sum\limits_{i=1}^n N_yi
  \end{equation*}\cite{NB}

  \item Support Vector machines (SVC)
  \begin{equation*}  
      sgn(\sum\limits_{i=1}^n y_i \alpha_i K(x_i, x) + \rho)    
  \end{equation*}\cite{SVC}
\end{itemize}

Each algorithm gives each comment a probability to be either positive or negative. 
We sum each algorithm's score and determine based on that score whether the comment is positive, negative or neutral. Below is a chart
showing the percentage of comments that were deemed positive, negative and neutral.

@@

\begin{figure}[h]
\centering
\begin{subfigure}{.25\textwidth}
 	\centering
	\includegraphics[width = .4\linewidth]{ThreadCount.png}
	\caption{Thread Count}
\end{subfigure}%
\begin{subfigure}{.25\textwidth}
 	\centering
	\includegraphics[width=.4\linewidth]{CommentCount.png}
	\caption{Comment Count}
\end{subfigure}
\caption{Thread and Comment Pie Charts}
\end{figure}
